%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Work Experience}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}
%---------------------------------------------------------
  \cventry
    {Software Engineer} % Job title
    {Leonardo Spa} % Organization
    {Pozzuoli, Italy} % Location
    {Oct. 2024 - now} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Radar Software Engineer for Leonardo Electronics division}
        \item {Contributed to CSCI code for the DFADR RAT31-DL Radar Processor in C++ to enhance radar data processing and system performance.}
        \item {Collaborated on the radar qualification process, authoring the Software Test Description (STD) and Software Design Description (SDD) documents to ensure compliance with system requirements and certification standards.}
        \item {Design of an automated testing tool in Python to streamline functional validation of the DFADR radar, significantly improving reusability and execution speed.}
        \item {Tools and frameworks: Docker, C++, CMake, Java Swing, Python}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Software Developer} % Job title
    {Intecs Spa} % Organization
    {Naples, Italy} % Location
    {Oct. 2023 - Oct. 2024} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Consultant for Hitachi Rail STS}
        \item {Conducted functional testing activities within the Automation 2.0 V\&V Product team, defining functional test specifications and managing non-conformities using RTC, GitLab, and Azure DevOps.}
        \item {Design and development of the back-end for the LogBook web application, to be integrated into the Automation 2.0 system for the ETIHAD RAIL STAGE 2 \& 3 project.}
        \item {Software full-stack development of the ATOR project, a web service aimed at automatically executing RBC and IXL tests through the use of Proxmox.}
        \item {Tools and technologies: Proxmox, Java Spring, JavaScript, MongoDB, jQuery, HTML, CSS, SQL, ActiveMQ, Mockito, Kubernetes}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Master Student} % Job title
    {University of Geneve - Département de physique nucléaire et corpusculaire} % Organization
    {Geneva, Switzerland} % Location
    {Mar. 2023 - Sep. 2023} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Development and testing of the digital peripheral for silicon sensors, using the SystemVerilog language and the UVM methodology.}
        \item {Relevant tools: Mermaid, GitLab, WaveDrom, Linux, Xcelium}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {University Tutor} % Job title
    {University of Naples Federico II} % Organization
    {Naples, Italy} % Location
    {Oct. 2022 - Jan. 2023} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Tutor for Mathematical Methods for Engineering and Fundamentals of Computer Science courses}
      \end{cvitems}
    }

%---------------------------------------------------------

\end{cventries}
